% Acknowledgement



I am lucky to have a large and supportive family and this dissertation would not have been possible without their encouragement, thank you all. I'd like to especially thank my parents, who taught me so much and always allowed me to make my own decisions without judgement. To my partner Paige and my cat Molly, thank you for making my life beyond math so much more joyful.  

To my committee; thank you Jarek and Lukas for giving me an appreciation of analysis and for skiing with me. Thank you Lisa for your work on Graduate Program Committee, I would not have attended MSU without it. Thank you Ryan and David, for being so involved with students and sharing your love of topology. David, thank you so much for all the time you spent working with me this past year, it has been tremendously impactful. 

I have made so many friends through mathematics and during my time in Bozeman. Anna, thank you for constantly reminding me of the joy of math, music, food, and life. Thank you Charlie, Dan, and Eric for the countless adventures. To all the wonderful people I have met through Big Sky Youth Empowerment, thank you for the inspiration and the opportunity to engage with our community in a meaningful way.

This work was completed through the mentorship of David Ayala.
It was partially supported by the National Science Foundation under awards 1812055 and 1945639.  
Some of this support was while David Ayala was in residence at the Mathematical Sciences Research Institute in Berkeley, California, during the Spring 2020 semester under Grant No. DMS-1440140.




